\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in,nofoot]{geometry}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{*1}{*1}

\newcommand{\entry}[4]{
  \noindent\textbf{#1} \hfill #2 \\
  \noindent\textit{#3} \hfill \textit{#4} \\
  \vspace{2pt}
}

\newcommand{\project}[2]{
  \noindent\textbf{#1} \hfill #2 \\
  \vspace{2pt}
}

\begin{document}

\pagenumbering{gobble}

\noindent
\begin{minipage}[t]{0.5\textwidth}
\textbf{\Large Eduardo Palhares}

\vspace{0.4em}

\noindent \faMapMarker ~ Cotia, Brazil \faUser ~ 27 years old \\
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\raggedleft
{\color{blue}} \href{mailto:eduardo@palharez.dev}{\faEnvelope \space eduardo@palharez.dev}

\vspace{0.2em}

{\color{blue}} \href{https://palharez.dev/}{\faGlobe \space Website} \quad
{\color{blue}} \href{https://github.com/palharez}{\faGithub \space GitHub} \quad
{\color{blue}} \href{https://linkedin.com/in/eduardopalhares}{\faLinkedin \space LinkedIn} \\
\end{minipage}

\vspace{0.5em}

\section*{Experience}
\vspace{0.6em}
\entry{Tenchi Security}{\faCalendar \space May 2024 -- present}{Backend Engineer}{\faMapMarker \space Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Developed an integration for retrieving data from Cloudflare, enhancing operational insights and accessibility.
\item Developed a data feed to integrate an internal API with Archer, enabling seamless data flow and functionality.
\item Maintained and developed an internal SDK/CLI, streamlining client integrations and improving developer experience.
\end{itemize}

\entry{xippTech}{\faCalendar \space June 2023 -- May 2024}{Software Developer}{\faMapMarker \space Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Developed an Odoo module for SLA and task recurrence management in helpdesk operations, improving service efficiency.
\item Generated translation files for individual modules, expediting project delivery timelines and enhancing localization.
\item Designed an activity workflow for insurance implementation control, ensuring streamlined processes and compliance.
\end{itemize}

\entry{Raízs}{\faCalendar \space September 2019 -- June 2023}{Software Developer}{\faMapMarker \space Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Developed an Odoo module for integration with the VTEX platform, streamlining data synchronization and operations.
\item Created an Odoo module for product markup calculations, enhancing sales efficiency and pricing accuracy.
\item Designed an Odoo module integrating the Juno service for automated boleto issuance, simplifying financial processes.
\item Built an integration service with the iFood supplier platform, enabling seamless data exchange and order management.
\item Developed a recommendation service for product substitution in shopping carts, optimizing user experience and inventory management.
\end{itemize}

\entry{Belga.io}{\faCalendar \space Jan 2019 -- September 2019}{Software Developer}{\faMapMarker \space Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Designed and implemented streamlined cryptocurrency arbitrage components leveraging JavaScript, Redis, WebSocket, and Docker for efficient market operations
\item Refactored and optimized legacy codebases, transitioning from Python to JavaScript, with an emphasis on performance enhancement and maintainability.
\item Developed new integrations for the open-source CCXT library, enabling expanded functionality and market connectivity.
\end{itemize}

\section*{Education}
\vspace{0.6em}
\entry{Universidade Anhembi Morumbi}{\faCalendar \space August 2023 -- present}{Bachelor's Degree, Computer Science}{\faMapMarker \space São Paulo}

\vspace{-0.6em}

\entry{ETEC - Escola Técnica Estadual de São Paulo}{\faCalendar \space January 2018 -- July 2019}{Technician, Information Technology}{\faMapMarker \space São Paulo}

\section*{Skills}
\vspace{0.6em}
\item \textbf{Languages:} \textbf{Native}: Portuguese | \textbf{Advanced}: English
\item \textbf{Technologies:} Python, Javascript, Typescript, SQL, NoSQL
\item \textbf{Developer Tools:} Git, AWS, GraphQL, RabbitMQ, Dpcker, Redis
\item \textbf{Frameworks:} NestJs, Express.js, Flask, Odoo, React.js

\end{document}